\documentclass[11pt]{scrartcl}
\usepackage[sexy]{../evan}
\usepackage{cmbright}
\usepackage{cancel}
\usepackage[T1]{fontenc}
%\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
%\usepackage[pdfborder={0 0 0},colorlinks=true,citecolor=red{}]{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{systeme}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathtools}
\SetStartEndCondition{ }{}{}%
\SetKwProg{Fn}{def}{\string:}{}
\SetKwFunction{Range}{range}%%
\SetKw{KwTo}{in}\SetKwFor{For}{for}{\string:}{}%
\SetKwIF{If}{ElseIf}{Else}{if}{:}{elif}{else:}{}%
\SetKwFor{While}{while}{:}{fintq}%
\newcommand{\forcond}{$i=0$ \KwTo $n$}
\SetKwFunction{FRecurs}{FnRecursive}%
\AlgoDontDisplayBlockMarkers\SetAlgoNoEnd\SetAlgoNoLine%


\title{CS 577: HW 1}
\author{Daniel Ko}
\date{Summer 2020}

\begin{document}
\maketitle

%problem 1
\section{
  Among the collection of n cards, is there a set of more than n/2 of them that are all
  equivalent to one another?
 }
\subsection{
	Present your algorithm and explain the notations as necessary.
}
\begin{algorithm}

	\KwData{cards, a collection of n cards; originalCards, the original/unmodified collection of n cards}
	\KwResult{A card such that more than $n/2$ are equivalent if it exists, else null.}
	\Fn{fraudMajority(cards)}{
		%\tcc{this is a comment to tell you that we will now really start code}
		\If{len(cards) $\leq$ 1 }{
			\Return cards[0]\;
		}\-\\
		left = fraudMajority(cards[0:floor(len(cards)/2)])\\
		right = fraudMajority(cards[floor(len(cards)/2):len(cards)])\\
		numOfLeft = originalCards.count(left)\\
		numOfRight = originalCards.count(right)\\
		\If{\text{numOfLeft > len(originalCards)/2}}{
			\Return left
		}
		\ElseIf{numOfRight > len(originalCards)/2}{
			\Return right
		}
		\Else{
			\Return null
		}
	}
\end{algorithm}



\subsection{
	Prove the correctness of your algorithm in making the final judgement regarding
	whether there exists a set of more than n/2 of cards that are all equivalent to one
	another.
}
\begin{proof}
	We show by strong induction that our algorithm is correct. Let $P(n)$ be the predicate,
	"fraudMajority halts and returns a card in a collection of $n$ cards
	such that more than $n/2$ are equivalent if it exists". We define $n \in \mathbb{N}$.
	\par \textbf{Base Case:} When $n = 0$, fraudMajority halts and returns null which is the correct output
	because the collection is empty. Hence, $P(0)$ holds.
	\par \textbf{Inductive step:} Suppose $P(n)$ holds for all $n \leq k \in \mathbb{N}$. We show that $P(k+1)$ holds.
	\par We observe that fraudMajority recursively calls collections of sizes $\floor{(k+1)/2}$ and
	$(k+1) - \floor{(k+1)/2}$.
	Since $\floor{(k+1)/2} \leq k$ and $(k+1) - \floor{(k+1)/2} \leq k $, we know by our strong inductive hypothesis that these
	recursive calls must halt. Hence, fraudMajority halts with an input of $k+1$ cards.
	\par fraudMajority finds the majority card of its left and right side, of size $\floor{(k+1)/2}$ and
	$(k+1) - \floor{(k+1)/2}$ respectively. Since both of these collections are less than $k$, by our strong inductive hypothesis,
	these recursive calls must return the correct output, the majority card of that partition if it exists.
	Then our algorithm calculates the total number of the majority card on the right and left on our
	$k+1$ collection and returns the majority. If no majority exists, it returns null. Thus,
	fraudMajority returns the correct output for a collection of $k+1$ cards.

	\par By strong induction, we have proven that $P(n)$ is true for all $n \in \mathbb{N}$.
	Therefore, fraudMajority is correct.
\end{proof}


%\subsubsection{Partial correctness}
%\begin{proof}
%	Suppose fraudMajority halts. 
%\end{proof}
%\subsubsection{Termination}

\subsection{
	Show the recurrence of the computing complexity and explain how did you obtain it.
	Note that you do not have to solve the recurrence since we can derive the solution
	using the Master’s theorem.
}
We claim that $T(n) = 2T(n/2) + 2n$ which is $\Theta(n\log n)$.
\begin{proof}
	Each call to our algorithm will result in two recursive calls
	with its input sized being halfed, which accounts for $2T(n/2)$. Additionally, calculating
	the number of originalCards will require $n$ time and we do this computation for both the left
	and right card, hence requiring an overall $2n$ time. The rest of the computations take constant time.
	Using the master theorem, it is clear that we get values of $a = 2, b = 2, d = 1$ for this particular
	recurrence which results in a complexity of $\Theta(n\log n)$.
\end{proof}



%problem 2
\section{Please describe an algorithm that finds a number that is
  bigger than any of its neighbors.}
  For brevity, we define a peak to be a number that is
  bigger than any of its neighbors.
\subsection{
	Present your algorithm and explain the notations as necessary.
}

\iffalse
\begin{algorithm}

	\KwData{arr, the $nxn$ matrix representing the grid of boxes}
	\KwResult{A number that is larger than its neighbors if it exists.}
	mid = floor(len(arr[0])/2) \\
	%row = len(arr)\\
	%col = len(arr[0])\\
	findLarge(arr, mid)\\
	\Fn{findLarge(arr, mid)}{
		max\_Col, max\_Col\_Index = maxColumn(arr, mid)\\
		\#Base Case: No local max number because we are checking the edges\\
		\If{mid $\leq$ 0 or mid $\geq$ len(arr[0]) - 1 or\\
		\ \ \ max\_Col\_Index $\leq$ 0 or max\_Col\_Index $\geq$ len(arr[0]) - 1 }{
			\Return null\\
		}\-\\
		\#Case 1: max\_Col is a local max, left and right are smaller\\
		\If{max\_Col > arr[max\_Col\_Index][mid - 1] and \\ \ \ \ max\_Col > arr[max\_Col\_Index][mid + 1]}{
			\Return max\_Col\\
		}\-\\
		\#Case 2: The number right of max\_Col is bigger, recursively call the right side\\
		\If{arr[max\_Col\_Index][mid + 1] > max\_Col}{
			\Return findLarge(arr, mid + floor(mid / 2))\\
		}\-\\
		\#Case 3: The number left of max\_Col is bigger, recursively call the left side\\
		\Return findLarge(arr, mid - floor(mid / 2))
	}

\end{algorithm}
\fi


\begin{algorithm}
\KwData{arr, the $nxn$ matrix representing the grid of boxes.}
\KwResult{A peak.}
\Fn{findLarge(arr)}{
	max $\leftarrow$ max element of boundary elements, middle row, and middle column\\
	\# Comparison is vacuously true for the neighbors that do not exist \\
	\If{max $>$ max's neighbors}{
		\Return max
	}
	%\If{size of arr $\leq 1x1$}{
	%	\Return null
	%}
	\# New submatrix does not contain the rows/columns used to find max\\
	recursive\_arr $\leftarrow$ the submatrix of the quadrant containing the largest neighbor \\
	\Return findLarge(recursive\_arr)
}
\end{algorithm}

\subsection{
	Prove the correctness of your algorithm in finding the right box that has a number
	that is larger than all its neighbors.
}
\begin{proof}
	We show by strong induction that our algorithm is correct. Let $P(n)$ be the predicate,
	"findLarge halts and returns a peak in a $nxn$ matrix".
	We define $n \in \mathbb{N^{+}}$.
	\par \textbf{Base Case:} When $n = 1$, findLarge halts the only element in the matrix, which by definition
	is larger than its neighbors, a peak. Hence, $P(1)$ holds.
	\begin{theorem*}
		A peak exists in any given matrix where its elements are unique integers. 
		\begin{proof}
			Let the set 
			containing all the unique integers in the matrix be $S = \{a_1, \cdots, a_\alpha\}$. 	
			Take set $S' = \{b_1, b_2, \cdots\}$ to be the upper bound of $S$, 
			where the upper bound is defined as $ \forall a_i \in S \ \ \forall b_j \in S', a_i \leq b_j$.
			Using the well ordering principle, there must exist as smallest element $b \in S'$.
			By definition, this must be the greatest element $a \in S$. 
			Hence, there exist a largest integer in a finite set of unique integers. 
			By definition, this largest integer is a peak. 	
		\end{proof}
	\end{theorem*}
	\begin{corollary*}
		There exists a peak in the submatrix of the quadrant containing the largest neighbor.
		\begin{proof}
			By previous lemma, there must exist a peak in the submatrix of the quadrant containing the largest neighbor
			because any subset of the original matrix containing unique elements, will have unique elements. Consider the 
			special case where the peak is on the edge of the new submatrix. Let $\alpha$ be the largest neighbor in the original 
			matrix and $\gamma$ be the max and peak on the edge. We know that $\gamma > \alpha$ because when we fix a max, 
			by definition it is the
			greatest integer in the boundary elements, middle row, and middle column. This directly implies that $\gamma$
			is greater than all its neighbors within the original matrix because of the fact that $\alpha$ was the
			greatest integer of the values that directly border the submatrix. 
		\end{proof}
	\end{corollary*}	
	\par \textbf{Inductive step:} Suppose $P(n)$ holds for all $n \leq k \in \mathbb{N}^{+}$. We show that $P(k+1)$ holds.
	
	\par We observe that findLarge recursively calls with an matrix of size 
	$\floor{(k-1) / 2} x \floor{(k-1) / 2}$.
	Since $\floor{(k-1) / 2} \leq k$, we know by our strong inductive hypothesis that this
	recursive call must halt. Hence, findLarge halts with a matrix of size $(k+1)x(k+1)$.
	
	\par If a peak does not exist in the boundary elements, middle row, and middle column, findLarge 
	recursively calls the submatrix with the biggest neighbor. By the corollary above, there 
	exist a peak in this submatrix. Since the size of the submatrix is $\floor{(k-1) / 2} x \floor{(k-1) / 2}$,
	and $\floor{(k-1) / 2} < k$, by our strong inductive hypothesis this recursive call returns a valid peak.

	\par By strong induction, we have proven that $P(n)$ is true for all $n \in \mathbb{N^{+}}$.
	Therefore, findLarge is correct.
\end{proof}

\subsection{
	Analyze the number of boxes that one need to open using your algorithm.
}
We claim that $T(n) = T(n/2) + 6n$ which is $\Theta(n)$.
\begin{proof}
	A call to our algorithm will result in single recursive call
	with its input sized being halfed, which accounts for $T(n/2)$.
\end{proof}

\end{document}

