\documentclass[11pt]{scrartcl}
\usepackage[sexy]{../../evan}
\usepackage{cmbright}
\usepackage{cancel}
\usepackage[T1]{fontenc}
%\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
%\usepackage[pdfborder={0 0 0},colorlinks=true,citecolor=red{}]{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{systeme}
\usepackage{verbatim}

\title{Math 240: Homework 9}
\author{Daniel Ko}
\date{Spring 2020}

\begin{document}
\maketitle

\section{1}
Let $A$ be any nonempty set. (You do not get to decide what $A$ is)
\begin{enumerate}[label=\alph*.]
\item{
	Let $R$ be a relation on $A$. Explain what is wrong with the following
	“proof” that if $R$ is symmetric and transitive, then it is reflexive.\par
	
	"Proof": Let $a \in A$. Take an element $b \in A$ such that $(a, b) \in R .$ Because $R$ is symmetric,
	we also have $(b, a) \in R$. Now using the transitive property, we can conclude that $(a, a) \in R$ because 
	$(a, b) \in R$ and $(b, a) \in R$
	\begin{proof}
		This proof is wrong because it assumes a priori that $(a, b) \in R$ when no such definition of the relation $R$ is 
		defined. 
	\end{proof}
}
\item{
	Give an example of a relation $R$ on $A$ which is symmetric and
	transitive, but not reflexive. Justify your answer.
	\begin{proof}
		The most trival example is a non empty set $A$ and the empty set $R$.   
		It is vacuously true that $R$ is symmetric and transitive.
		However, $R$ is not reflexive because there are no relations in it,
		i.e. the following statement does not hold: $\forall a \in A : (a,a) \in R$.
	\end{proof}
}
\end{enumerate}

\section{2}
Give an example of a relation $R$ on $\mathbb{N}$ such that if $S$ is a relation on $\mathbb{N}$
which contains $R$, then $S$ is not antisymmetric. Justify your answer.
(This implies that the antisymmetric closure of R does not exist.)
\begin{proof}
Consider the relation $R = \{(1,2),(2,1)\}$. It is clear that $1 \neq 2$, hence $R$ is 
not antisymmetric. Therefore, if $S$ contains $R$, then $S$ is not antisymmetric.
\end{proof}

\section{3}
Come up with a topological ordering of the following DAG, i.e., write
down the vertices in some order such that if $(i, j)$ is an edge, then $i$ is
to the left of $j$.
\begin{proof}
Using Kahn's algorithm, we get the topological ordering of 
$2,3,4,6,1,5$.
\end{proof}

\section{4}
Let $R$ be the relation on $\mathbb{R}$ defined by $(x, y) \in R$ if and only if $x - y$
is rational. Is $R$ symmetric? Antisymmetric? Reflexive? Transitive?
Justify your answers. (You may use basic properties about rational
numbers without proving them)
\begin{proof}\
	\begin{enumerate}[label=\alph*.]
		\item{
			R is symmetric\par
			This is because there is closure under addition/subtraction for rational numbers.
			If $x - y$ is a rational number then $y - x$ is a rational number, hence 
			$(y,x) \in R$. 
		}
		\item{
			R is not antisymmetric \par
			Consider the following relation in $R$: $(1,2)$ and $(2,1)$.  
			It is clear that $1 \neq 2$. Therefore, $R$ is not antisymmetric.
		}
		\item{
			R is reflexive \par
			Suppose $x \in \mathbb{R}$. Any number subtracted by itself will be zero.
			Zero is a rational number. Thus, $(x,x) \in R$. Therefore, R is reflexive.
		}
		\item{
			R is transitive \par
			Suppose $(x,y)$ and $(y,z)$ are in R. This means that $x - y$ and $y - z$ are rational
			numbers. Now consider,
			\begin{align*}
				x - z & = (x - y) + (y - z)
			\end{align*}
			Since there is closure under addition for rational numbers, $x - z$ must be a rational number.
			Hence, $(x,z) \in R$. Therefore, R is transitive.
 		}
	\end{enumerate}
\end{proof}

\section{5}
Let $R$ be a relation on a set $A$. Prove that if $R$ is reflexive, then $R \subseteq R^n$
for all $n \geq 1$.
\begin{proof}
	yeet
	
\end{proof}

\begin{comment}

Prove that in any group of $n$ people $(n \geq 2),$ there must be two people with the same number of friends within the group. Assume friendship
is mutual, and nobody is their own friend. 
\begin{proof}
	Given that there is $n$ people, the amount of friends each person will be in this set: $\{0,1,\cdots, n-1\}$, excluding $n$
	because you cannot be friends with yourself. Consider the case when someone has $n-1$ friends. This means everyone in this group
	has at least one friend. Also consider the case when someone has $0$ friends. This means that the most amount of friends one can
	have is $n-2$ because you cannot be friends with yourself and with the person with $0$ friends. Thus the range of friends that 
	a group has is actually $\{1,2,\cdots, n-1\}$ or $\{0,1,\cdots, n-2\}$. In both cases, the number possible combination of friends 
	one can have is $n-1$. Using the pigeonhole principle, it directly follows that there must exist at least 2 people with the same 
	number of friends in this group. 
\end{proof}
\begin{enumerate}[label=\alph*.]
	\item{
	      Let $T$ be a tree. Prove that if you remove a leaf $l$ and the only edge incident with $l$ from $T$,
	      the resulting subgraph $T^{\prime}$ is still a tree.
	      \begin{proof}
		      Since $T$ is a tree, it is by definition acyclic and connected. We must show that $T'$
		      holds the property of a	tree.
		      \begin{enumerate}[label=\roman*.]
			      \item{
			            $T'$ is connected \par
			            From lecture, we know that a graph is connected if and only if there is a simple path between
			            every two distinct vertices. If we removed a leaf and only its edge incident, we know that
			            this cannot affect any simple path from $\{u,v\}$ in the tree. Thus, the resulting tree, $T'$,
			            is connected.
			            }
			      \item{
			            $T'$ is acyclic \par
			            If $T$ is acylic, removing a vertex will not make it cyclic.
			            }
		      \end{enumerate}
		      Therfore, $T'$ is a tree.
	      \end{proof}
	      }
	\item{
	      Prove by induction on $n \geq 1$ that if a tree $T$ has $n$ vertices, then
	      it has exactly $n-1$ edges.
	      \begin{proof}
		      We proceed by induction on  $n \geq 1$. Let $P(n)$ be the predicate
		      "if a tree $T$ has $n$ vertices, then it has exactly $n-1$ edges".\\
		      \textbf{Base case:} We prove that $P(1)$ holds. This means that $T$
		      has $1$ vertex. It trivially follows that $T$ has $0$, i.e. $n-1 = 1 - 1 $ edges. \\
		      \textbf{Inductive step:} Suppose that $n \geq 1$ such that $P(n)$ holds. We prove that $P(n + 1)$ holds.
		      Let $T = (V,E)$ be the tree with $n$ vertices. We know that the tree with $n+1$ edges, $T'$,
		      will have a set of vertices $V' = V \cup \{u\}$, where $u$ is a vertex. Since $T'$ is a tree,
		      $u$ adds only one edge. If it is placed as a leaf, then $u$ there is a new edge create from $u$ to its
		      parent. If it is placed in the middle of the tree, the existing edge between the adjacent vertex will
		      be used as one of the edges connecting $u$ and another edge must be added to finish connecting $u$ to the tree.
		      So in either case, adding a new vertex only adds one edge. It follows then by this fact and by our induction hypothesis that
		      \begin{align*}
			      \sum_{v \in V'} \operatorname{deg}(v) & = \sum_{v \in V} \operatorname{deg}(v) + \operatorname{deg}(u) \\
														& = n - 1 + \operatorname{deg}(u)  \\
														& = n - 1 + 1 \\
														& = n
			  \end{align*}
			  Therefore, $P(n+1)$ holds and this concludes our inductive step. 
			  We have proved by induction that for all $n \geq 1$ that if a tree $T$ has $n$ vertices, then
			  it has exactly $n-1$ edges.
	      \end{proof}
	      }
	\item{
	      Prove that if $G$ is a connected graph with $n$ vertices, then it has at least $n-1$ edges. (Hint: Spanning tree.)
		 \begin{proof}
			We know that a graph is connected if and only if it has a spanning tree (theorem given in the lecture).
			Thus, that $G$ is a spanning tree. It directly follows from this fact and from part (b) that $G$ has exactly $n-1$
			edges.
		 \end{proof} 
		  }
\end{enumerate}
\end{comment}

\end{document}
