\documentclass[11pt]{scrartcl}
\usepackage[sexy]{../evan}
\usepackage{cmbright}
\usepackage{cancel}
\usepackage[T1]{fontenc}
%\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
%\usepackage[pdfborder={0 0 0},colorlinks=true,citecolor=red{}]{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{systeme}
\usepackage[vlined]{algorithm2e}
\usepackage{mathtools}
\SetStartEndCondition{ }{}{}%
\SetKwProg{Fn}{def}{\string:}{}
\SetKwFunction{Range}{range}%%
\SetKw{KwTo}{in}\SetKwFor{For}{for}{\string:}{}%
\SetKwIF{If}{ElseIf}{Else}{if}{:}{elif}{else:}{}%
\SetKwFor{While}{while}{:}{fintq}%
\newcommand{\forcond}{$i=0$ \KwTo $n$}
\SetKwFunction{FRecurs}{FnRecursive}%
\AlgoDontDisplayBlockMarkers\SetAlgoNoEnd\SetAlgoNoLine%


\title{CS 577: HW 5}
\author{Daniel Ko}
\date{Summer 2020}

\begin{document}
\maketitle

\section{
  Joe is a project manager in a software company called SuperDuo. Joe found out that
  programmers usually produces the highest quality codes when they are working in pair.
  However, the productivity of each pair of programmers is the speed of the slower
  programmer. So Joe needs to figure out the best strategy for pairing the programmers to
  generate the maximum sum of productivity for his project. Suppose that the number of
  programmers in Joe’s project is even.
 }

\subsection{
	Give a greedy strategy that maximizes the sum of the productivity of all
	pairs. You should describe the greedy strategy first and then write it in the form of an
	algorithm. Also you should analyze the computing complexity of the greedy
	algorithm.
}
The greedy strategy is to first sort the programmers in ascending order of productivity.
Then, we pair the first two programmers, then the next two, etc. We sum up all the
slower programmer in each pair, which will be our maximum sum of productivity.
\begin{algorithm}
	\KwData{A list $gamer$ of even size $n$, containing the productivity level of each programmer}
	\KwResult{The maximum sum of productivity for pair programming}
	\Fn{maxProd($gamer$)}{
		sortedGamer $\leftarrow$ Sort $gamer$ in ascending order of productivity\\
		totalProd $\leftarrow$ 0\\
		\For{int i = 0; i < n; i+=2}{
			totalProd += sortedGamer[i]
		}
		\Return{\text{\normalfont totalProd}}
	}
\end{algorithm}\\
The time complexity of maxProd is $O(n\log n)$
\begin{proof}
	We first sort the list gamer of size $n$. Using an efficient sorting algorithm such as
	merge sort, this will take $O(n\log n)$ time. Then, we sum up every other element
	in the list, which takes $O(n)$ time. The rest of the computations take constant time.
	Hence, the total time complexity is $O(n\log n + n) = O(n\log n)$
\end{proof}
\subsection{
	Prove that this greedy strategy indeed generates the maximum sum of
	productivity.
}
We will use a “Greedy Stays Ahead” argument to prove this greedy strategy.
\subsubsection{
	Define Your Solution
}
Let $A=\{a_1, a_2, \cdots, a_{n/2}\}$ denote the pairs containing the productivity values of two programmers
that our algorithm will generate, i.e. $a_i = (p_\alpha, p_\beta)$ where $p_\alpha$ and $p_\beta$ are the
productivity values of $\alpha$ and $\beta$th lowest productive programmer in this $i$th pair respectively.
Let $O = \{o_1, o_2, \cdots, o_{n/2}\}$ denote the pairs containing the productivity values of two programmers
that an optimal algorithm will generate. Let $O$ be ordered in ascending productivity, i.e. if $i>j$,
the productivity of pair $o_i$ will be equal to or higher than pair $o_j$.
\subsubsection{
	Define Your Measure
}
For our algorithm, let $\delta(a_1), \cdots, \delta(a_{n/2})$ denote the total productivity of pairs
from $a_1$ to $a_i$. For example, $\delta(a_3)$ will be the sum of the productivity (the
lower productivity between the two programmers) of pairs $a_1$, $a_2$, and $a_3$.
Formally, we can express this function as
$$\delta(a_i) = \sum_{j=1}^i \min(a_j)$$
Similiary for the optimal algorithm, the $\delta(o_1), \cdots, \delta(o_{n/2})$ denote
the total productivity of pairs from $o_1$ to $o_i$.
\subsubsection{
	Prove Greedy Stays Ahead
}
We show by induction that our greedy stays ahead.
\begin{proof}
	Let $P(i)$ be the predicate, "$\delta(a_i) \geq \delta(o_i)$"
	We define $i \in \mathbb{N}^+$. \\
	\textbf{Base Case:} When $i = 1$, we know that $a_1$ contains the lowest productivity programmer
	because we paired up the two lowest productivity programmers in our algorithm. We also know that
	$o_1$ contains the lowest productivity programmer because we ordered $O$ in ascending productivity.
	The least productive pair must contain the lowest productivity programmer because the
	productivity any pair containing the lowest productivity programmer will the productivity value of the
	lowest productivity programmer.
	Hence, the productivity of pair $a_1$ will be the value of lowest productivity programmer, and
	similarly, the productivity of pair $o_1$ will be the value of lowest productivity programmer.
	Thus, $\delta(a_1) \geq \delta(o_1)$ and $P(1)$ holds.\\
	\textbf{Inductive step:} Suppose $P(k-1)$ holds. We show that $P(k)$ holds.
	By our algorithm, we know that pair $a_k$ contains the $(2k-1)$th lowest productive
	programmer and $a_k$'s productivity value will be the productivity value of the
	$(2k-1)$th lowest productive programmer, i.e. $\min(a_k) = p_{2k-1}$.
	We claim that we can bound the productivity value of pair $o_k$ by
	%$p_k \leq 
	$\min(o_k) \leq p_{2k-1}$. We know that since $O$ is ordered
	in ascending productivity, the productivity value of pair $o_k$ must be equal or greater
	to the pairs that came before it. There are $2k-2$ programmers that come before pair
	$o_k$. This means that at most, there are $2k-2$ programmers with lower or equal productivity value
	than productivity value of pair $o_k$ from the pairs behind $o_k$.
	If we include the programmer that determines the productivity value of pair $o_k$,
	we have $2k-1$ programmers with lower or equal productivity value
	than productivity value of pair $o_k$. It follows from the pigeonhole principle
	that $\min(o_k) \leq p_{2k-1}$ because if $\min(o_k) \geq p_{2k}$ then
	there would exist some programmer with productivity value equal or
	less than $p_{2k-1}$ that will not belong in the pairs behind $o_k$ but
	rather ahead of $o_k$, which would be a contradiction because $O$ is
	ordered, i.e. $p_{2k}$ will appear before $p_{2k-1}$.
	Using this bound we know that $\min(a_k)\geq \min(o_k)$ and by our induction
	hypothesis we know that $\delta(a_{k-1}) \geq \delta(o_{k-1})$. It follows that,
	\begin{align*}
		\delta(a_k) & = \delta(a_{k-1}) + \min(a_k)    \\
		            & \geq \delta(o_{k-1}) + \min(o_k) \\
		            & \geq \delta(o_k)
	\end{align*}
	$P(k)$ holds as desired. Therefore by induction, $\delta(a_i) \geq \delta(o_i)$ for all $i \in \mathbb{N}^+$.
\end{proof}


\subsubsection{
	Prove Optimality
}
Since both $O$ and $A$ have the same number of pairs, $n/2$, it follows from our proof
from 1.2.3 that $\delta(a_{n/2}) \geq \delta(o_{n/2})$. Therefore, our algorithm is
optimal because
the total productivity of $A$ is equal or greater than the total productivity of
$O$.

\section{
  Give an algorithm that increases the lengths of certain edges so that
  the resulting tree has zero skew and the total edge length is as small as
  possible.
 }

\subsection{
	Describe a greedy strategy and write it in the algorithm format. Also
	analyze the computing complexity of the algorithm.
}
Suppose we have a complete balanced binary tree, $T$, with root $v$ 
and child nodes $l$ and $r$. Let $\delta_l$ be maximum distance between
the paths that start at the root of $T$ and ends on leaf that is a child of $l$. 
Similiarly, let $\delta_r$ be the maximum distance between
the paths that start at the root of $T$ and ends on leaf that is a child of $r$. 
If $\delta_l > \delta_r$, add $\delta_l - \delta_r$ to the edge between
$v$ and $r$. 
If $\delta_r > \delta_l$, add $\delta_r - \delta_l$ to the edge between
$v$ and $l$.
If $\delta_r = \delta_l$, do nothing. Recursively call this algorithm
on the child nodes, $l$ and $r$, until there are no more child nodes to call. 
\iffalse
\begin{algorithm}
	\KwData{$T = (V,E,\ell)$, a complete balanced binary tree with an associated edge length}
	\KwResult{A tree has zero skew and the total edge length is as small as	possible}
	\Fn{timingCircuit($T$)}{
		\For{$v \in V$ in level order traversal}{
			\#$l$, $r$ is left, right child of $v$ respectively\\
			\If{$l$ and $r$ exists}{
				$\delta_l \leftarrow$  
				max(paths that start at the root of $T$ and ends on leaf that is a child of $l$) \\
				$\delta_r \leftarrow$  
				max(paths that start at the root of $T$ and ends on leaf that is a child of $r$) \\
				\# Where $\ell_{(a,b)}$ is the associated length of edge $(a,b) \in E$\\  
				\If{$\delta_l > \delta_r$}{
					Increment $\ell_{(v,r)}$ by $\delta_l - \delta_r$  
				}
				\ElseIf{$\delta_r > \delta_l$}{
					Increment $\ell_{(v,l)}$ by $\delta_r - \delta_l$
				}
			}
		}
		\Return{$T$}
	}
\end{algorithm}
\fi

\begin{algorithm}
	\KwData{$T = (V,E,\ell)$, a complete balanced binary tree with an associated edge length\\
	\qquad \hspace{0.5em} $v \in V$,  }
	\KwResult{Length from root to leaf (zero skew value); a tree has zero skew and the total edge length is as small as	possible}
	\Fn{timingCircuit($v$)}{
		\If{$v$ is a leaf}{
			\Return{0}
		}
		$\delta_l = $ timingCircuit($l$)\\
		$\delta_r = $ timingCircuit($r$)\\
		%$\ell_{L} =$ edge length of $v$ to $L$ \\
		%$\ell_{R} =$ edge length of $v$ to $R$ \\
		\# Where $\ell_{(a,b)}$ is the associated length of edge $(a,b) \in E$\\  
		\If{$\delta_l + \ell_{(v,l)} > \delta_r + \ell_{(v,r)}$}{\-\\
			Increment $\ell_{(v,r)}$ by $(\delta_l + \ell_{(v,l)}) - (\delta_r + \ell_{(v,r)})$  
		}
		\ElseIf{$\delta_r + \ell_{(v,r)} > \delta_l + \ell_{(v,l)}$}{\-\\
			Increment $\ell_{(v,l)}$ by $(\delta_r + \ell_{(v,r)}) - (\delta_l + \ell_{(v,l)})$
		}
		\Return{$\delta_r + \ell_{(v,r)}$}
	}
\end{algorithm}
The time complexity of timingCircuit is $\Theta(n)$.
\begin{proof}
	Each recursive call in our algorithm halves the input size and we have two 
	recursive calls. The rest of the computations take constant time.  
	We get a recurrence relationship of $T(n) = 2T(n/2) + n^0$ 
	which is $\Theta(n)$ by the master theorem.
\end{proof}
\subsection{
	Prove that this greedy strategy indeed generates the optimal solution
}
\begin{lemma}
	The algorithm timingCircuit will always generate a zero skew tree. 	
\end{lemma}
\begin{proof}
	We show by strong induction that timingCircuit will always generate a zero skew tree. 	
	Let $P(n)$ be the predicate "timingCircuit will generate a zero skew tree that has $n$ leaves".
	We define $n \in \mathbb{N}^+$. \\
	\textbf{Base Case:} When $n = 1$, timingCircuit returns $0$. It is trivially true 
	that a tree with a single node will always have zero skew. Hence $P(1)$ holds.\\
	\textbf{Inductive step:} Suppose for all $1 \leq n \leq k$, $P(n)$ holds. We show that $P(k+1)$ holds.
	We know that the subtrees generated by the children of $v$, $l$ and $r$, will have strictly less  
	leaves than $k+1$. It follows by our strong inductive hypothesis, that timingCircuit($l$) and timingCircuit($r$)
	will correctly generate a zero skew subtrees for the subtrees that have $l$ and $r$ has its root,
	and return the distance from $l$ to its leaves, $\delta_r$, and $r$ to its leaves, $\delta_l$.  
	Since the two subtrees generated by the children $v$ are zero skew, all we need to do so that 
	the entire tree is zero skew is to 
	modify the edge length between $(v,l)$ and $(v,r)$ such that  
	$\delta_r + \ell_{(v,r)} = \delta_l + \ell_{(v,l)}$, i.e. both subtrees have same zero skew 
	if we start from $v$. This is exactly what we do in the if and else if statement in our algorithm.
	Hence, timingCircuit generates a zero skew tree that has $k+1$ leaves and $P(k+1)$ holds. 
	Therefore by strong induction, timingCircuit will always generate a zero skew tree.
\end{proof} 

We define terms for the following theorem.
Let $T$ be the original tree and let $\ell$ be its associated edge length. 
Let $v$ be the root of $T$ and let $l$ and $r$ be the left and right child of $v$ respectively. 
Let $T_\alpha$ be the tree generated by timingCircuit. Let $T_\phi$ be an 
optimal tree, i.e. a zero skew tree such that the total edge length is as small as possible.
Let the left and right subtree of $T_\alpha$ be $L_\alpha$, $R_\alpha$.
Similiarly, define $L_\phi$, $R_\phi$. 
Let $\ell^\alpha$ and $\ell^\phi$ and the associated edge length of $T_\alpha$ and $T_\phi$ respectively.

\iffalse
\begin{lemma}
	If $L_\alpha = L_\phi$ and $R_\alpha = R_\phi$,	then $\ell^\alpha_{(v,l)} \leq \ell^\phi_{(v,l)}$ and 
	$\ell^\alpha_{(v,r)} \leq \ell^\phi_{(v,r)}$.
\end{lemma}
\begin{proof}
	Consider the case when $\delta_l + \ell_{(v,l)} > \delta_r + \ell_{(v,r)}$.
	We show $\ell^\alpha_{(v,l)} \leq \ell^\phi_{(v,l)}$ and 
	$\ell^\alpha_{(v,r)} \leq \ell^\phi_{(v,r)}$.
	Suppose for the sake of contradiction, $\ell^\alpha_{(v,l)} > \ell^\phi_{(v,l)}$.

\end{proof}
\fi
\begin{theorem}
	The algorithm timingCircuit will always generate a unique zero skew tree such that the 
	total edge length is as small as possible.
\end{theorem}
\begin{proof}
	From lemma 2.1, we know that timingCircuit will always generate a zero skew tree. 
	It is sufficient to show that timingCircuit will minimize total edge length when
	generating this tree. %We show by an exchange argument that timingCircuit is optimal.
	%Suppose $T_\alpha \neq T_\phi$, where T_\phi. There must exist an edge $(a,b) \in E$ 
	Suppose $T_\alpha$ is not an optimal solution, i.e. total edge length of $T_\phi$ 
	is strictly less than total edge length of $T_\alpha$.
	This means there exists an edge $(a,b)$ such that $\ell^\alpha_{(a,b)} < \ell^\phi_{(a,b)}$.
	Fix $(a,b)$ such that it is the closet edge from the leaves. 
	
	%This means that the edge length on the 
	%original tree, $\ell_{(a,b)}$, must of increased by at least $\ell^\phi_{(a,b)} - \ell^\alpha_{(a,b)}$ .
\end{proof}







\iffalse
We will use an exchange argument argument to prove this greedy strategy
\subsubsection{
	Define Your Solution
}
Let $T_g = (V, E, \ell^g)$ be the tree generated by our greedy algorithm, where $\ell^g$
is the associated edge length of $T_g$.   
Let $T_o = (V, E, \ell^o)$ be a tree that is 
generated by an optimal algorithm where $T_o$ has zero skew and the total edge length is as small as possible.




\subsubsection{
	Compare Solutions
}
If $\ell^g \neq \ell^o$, there exists an edge $(a,b) \in E$ such that $\ell^g_{a,b} \neq \ell^o_{a,b}$.

\subsubsection{
	Exchange Pieces
}
\subsubsection{
	Iterate
}
\fi
\end{document}

